---
title: "User Time Log report"
author: "NBIS Support Manager group"
date: today
always_allow_html: true
format: 
  confluence-html:
    self-contained: true
    page-layout: full
params: # Change to fit your query
  params_file: timeLogParams.yaml
execute:
  freeze: false
---

```{r setup, include=FALSE}
library(knitr)
library(reticulate)
library(yaml)
knitr::opts_chunk$set(echo = FALSE)

cwd = getwd()
base = dirname(cwd)
lib_path = file.path(base,"lib") 

# Find the absolute path to the Python executable managed by Pixi
pixi_env_path = Sys.getenv("CONDA_PREFIX", unset = "")
if (pixi_env_path != "") {
  # Use the Python executable inside the activated Pixi/Conda environment
  reticulate::use_python(file.path(pixi_env_path, "bin", "python"), required = TRUE)
} else {
  # If CONDA_PREFIX is not set, try to use the environment name
  python_path = file.path(base,".pixi/envs/default/bin/python") 
  reticulate::use_python(python_path, required=T )
  warning("CONDA_PREFIX environment variable not set. Please ensure you knit from a 'pixi shell'.")
}
# Read all params
myparams = read_yaml(params$params_file)
```

```{r correspond}
# Define how to group Redmine Activities
corr = data.frame(
  redmine=I(list(
    "Absence (Vacation/VAB/Other)",                         # Absence
    "Administration",                                       # Administration
    "Internal NBIS",                                        # Internal NBIS
    c("NBIS Management", "Management"),                     # Coordination
    c("Development", "Internal consultation", "Outreach"),  # Community
    "Professional Development",                             # Professional development
    c("Consultation", "Support", "Internal consultation"),  # Support
    "Training"                                              # Training
  )), 
  row.names=c(
    "Absence",
    "Administration",
    "Internal NBIS",
    "Coordination",
    "Community", 
    "Professional Development",
    "Support",
    "Training"
  )
)

presence = c("Administration", "Internal NBIS", "Coordination", "Community", "Professional Development", "Support", "Training")
output = c("Consultation", "Coordination","Community", "Support", "Training")

approxJobYear = 1983 #hours
approxWorkYear = 1700 #hours

fracYear = as.numeric(as.Date(myparams$end_date) - as.Date(myparams$start_date))/365
approxJobHours = approxJobYear * fracYear
```

## Introduction

The time logging categories from RedMine are grouped into useful categories as follows:

```{r corrtable, echo=FALSE}
# Display how we group the redmine activites
corr2 = corr
corr2$redmine = lapply(corr2$redmine, paste, sep=";")
kable(corr2)

```

Three different pie-charts/table approaches are shown.

1. **Presence/absence** Meant only to give an overview to visualize reduced work time etc. -- not to be used to stress experts.
Notice that _absence_ include several subcategories, vacation, VAB, Sick leave, Parental leave, etc, but that reporting these are optional in LTS.
The PercentExp denotes percent of approximate expected yearly work time, here this is set to `r approxJobYear`. 

2. **Distribution of presence time on different categories** (see table).

3. **Distribution of presence time on _output_** Output = (`r paste(output, sep=",")`).

(kudos to Henrik)

<div class=pgbr>

```{python redmine, echo=FALSE, eval=TRUE}
# make the redmin_utils lib directory available for imports, 
# to be able to import Redmine_apis.py from there
import sys
sys.path.append(str(r.lib_path))   

# Get the records from Redmine
from Redmine_apis import *
import pandas as pd
import yaml
import datetime

# Load Redmine credentials from YAML config file
with open(r.myparams['config_file'], 'r') as config_file:
    config = yaml.safe_load(config_file)

# Open Redamine API
redmine = Redmine_server_api(config)

# Use any dummy projects from Redmine to set up user db indexed by user id
project_name = 'Long-term Support'
project_id = redmine.find_project_id_from_name(project_name)
userNameToId = redmine.create_user_name_to_id(project_id)

pyparams = r.myparams # r.myparams["users"] appears to be immutable in this chunk
# Handle empty user list
if(pyparams["users"] == None):
  pyparams["users"] = list(userNameToId.keys())
# Handle single use in list
if(isinstance(pyparams["users"], list) == False):
  pyparams["users"] = [ pyparams["users"] ]

allTimeLog = {}
allTimeLogIssue = {}
deletedUsers = []
for user in pyparams["users"]: 
  if(not user):  # Only actual users will be handled
    deletedUsers.append(user)
    continue
  user_id = userNameToId[user]
  userTimeLog =  pd.DataFrame.from_dict(
    redmine.report_time_entries_by_activity_and_month(
      user_id, pyparams["start_date"], pyparams["end_date"]),
      orient='index')
  ordCols = sorted(userTimeLog.columns)
  # An ineffective way of getting rid of people that have quit, or more
  # precisely, people who have not logged time in the requested time interval
  if(userTimeLog.empty == False):
    userTimeLog["Activity"] = userTimeLog.index
    allTimeLog[user] =  userTimeLog[ ["Activity"] + ordCols ]
    userIssueTimeLog = pd.DataFrame.from_dict(
      redmine.report_time_entries_by_issue(
        user_id, 
        pyparams["start_date"], 
        pyparams["end_date"]
        ), orient='index')
    allTimeLogIssue[user] =  userIssueTimeLog.sort_values(
      by=['Project', 'Tracker', 'Total time'],
      ascending = False)
  else:
    deletedUsers.append(user)
pyparams["users"] = [ a for a in pyparams["users"]  if a not in deletedUsers ]
r.myparams = pyparams # ...but you are allowed to change the whole of r.myparams -- strange!
pyparams = None # clear in case this duplicate is really big
```

```{r visualize, results='asis'}
library(kableExtra) 

for(key in myparams$users){ 
  cat(paste0(
    "\n## Summary of time logging for the period",
    myparams$start_date," -- ", myparams$end_date,"\n")
    )
  cat(paste("##", key, "\n"))
  raw = data.frame(py$allTimeLog[key], 
                   stringsAsFactors=TRUE, 
                   check.names = FALSE )
  names(raw) = sapply(names(raw), function(x) sub(paste0(key, "."), "", x))
  raw[is.na(raw)] <- 0
  ret = data.frame("Activity"=character(), "Time"= double())
  for(i in row.names(corr)){
    ret = rbind(
      ret,
      data.frame("Activity"= i, 
                 "Time" = sum(raw[raw$Activity %in% unlist(corr[i,"redmine"]),
                                  "Total time"])
                 )
      )
  }
  # Presence/absence
  cat('<div class="columns">\n')
  curr = ret[ret$Activity == "Absence", ]
  curr = rbind(
    curr, 
    data.frame(Activity = "Presence", 
               "Time" = sum(ret[ret$Activity %in% presence, "Time"])
               )
    )
  curr$Percent = round(curr$Time/sum(curr$Time) * 100, 2)
  curr$PercentExp = round(curr$Time/approxJobHours * 100, 2)
  cat('<div class="column" width="70%">\n')
  pie(
    curr$Time, labels=curr$Activity, 
    main=paste("Absence/presence pie chart for", key)
    )
  cat('</div>\n')
  curr = rbind(
    curr, 
    data.frame(
      Activity= "Total", 
      Time = sum(curr$Time), 
      Percent = sum(curr$Percent), 
      PercentExp = sum(curr$PercentExp)
      )
    )
  cat('<div class="column" width="30%">\n')
  print(kable(curr,  row.names = FALSE, "html") %>% 
          kable_styling("condensed", full_width=F))
  cat('</div>\n')

  # Presence
  curr = ret[ret$Activity %in% presence, ]
  curr$Percent = round(curr$Time/sum(curr$Time) * 100, 2)
  cat('<div class="column" width="70%">\n')
  pie(
    curr$Time, 
    labels=curr$Activity, 
    main=paste("Presence Time pie chart for", key)
    )
  cat('</div>\n')
  curr = rbind(
    curr, 
    data.frame(Activity= "Total", Time = sum(curr$Time), 
               Percent = sum(curr$Percent))
    )
  cat('<div class="column" width="30%">\n')
  print(kable(curr, row.names = FALSE, "html") %>% 
          kable_styling("condensed", full_width=F))
  cat('</div>\n')

  # output
  curr = ret[!ret$Activity %in% c(output, "Absence"),]
  curr=rbind(
    curr, 
    data.frame(
      Activity="Output", 
      Time = sum(ret[ret$Activity %in% output, "Time"])
      )
    )
  curr$Percent = round(curr$Time/sum(curr$Time) * 100, 2)
  cat('<div class="column" width="70%">\n')
  pie(
    curr$Time, 
    labels=curr$Activity, 
    main=paste("Output pie chart for", key)
    )
  cat('</div>\n')
  curr = rbind(
    curr, 
    data.frame(Activity= "Total", Time = sum(curr$Time), 
               Percent = sum(curr$Percent) )
    )
  cat('<div class="column" width="30%">\n')
  print(kable(curr, row.names = FALSE, "html") %>% 
          kable_styling("condensed", full_width=F))
  cat('</div>\n')
  cat('</div>\n')

  # Full Time Log distributed over months  
  cat(paste(
    "### Full Time Log distributed over activities and months for", 
    key,"\n"
    ))
  print(kable(raw, row.names = FALSE, "html") %>% 
          kable_styling("condensed", font_size = 10, full_width=F))

  # Full Time Log distributed over issues
  raw = data.frame(py$allTimeLogIssue[key], 
                   stringsAsFactors=TRUE, 
                   check.names = FALSE)
  names(raw) = sapply(names(raw), function(x) sub(paste0(key, "."), "", x))
  cat(paste("### Full Time Log distributed over issues for", key,"\n"))
  print(kable(raw, row.names = TRUE, "html") %>% 
          kable_styling("condensed", font_size = 10, full_width=F))

  # Warn about activities not in the current correspondence table
  for(i in unique(raw$Activity)){
    if(!i %in% redmine){
      print(paste0("New activity, ", i, ", found; please include in variable 'corr'\n"))
    }
  }
}
```
</div>
